Models

### 2022-04-20 analysis/05_model_metrics.Rmd
Modify reading files in to be cleaner

Get list of models that couldn't be fit due to model limitations 
```{r}
#models that were fit
uniq_metric_model <- metric_model_table %>% select(metric, model_id) %>% distinct()
#models we attempted to fit
uniq_mods <- mods %>% select(metric, model_id) %>% distinct()

setdiff(uniq_mods, uniq_metric_model)
```

>>>>

Get list of models that couldn't be fit due to model limitations 
```{r}
#models that were fit
uniq_metric_model <- metric_model_table %>% select(metric, model_id) %>% distinct()
#models we attempted to fit
uniq_mods <- mods %>% select(metric = metric_name, model_id) %>% distinct()

missing_mods <- setdiff(uniq_mods, uniq_metric_model)
```
